Robust self-testing of large entanglement with constant-sized correlations

### 2019-04-29 Draft/draft.tex
Honghao: finished section 6

% Clever references
\usepackage{cleveref}%[nameinlink]
\crefname{lemma}{Lemma}{Lemmas}
\crefname{proposition}{Proposition}{Propositions}
\crefname{definition}{Definition}{Definitions}
\crefname{theorem}{Theorem}{Theorems}
\crefname{conjecture}{Conjecture}{Conjectures}
\crefname{corollary}{Corollary}{Corollaries}
\crefname{claim}{Claim}{Claims}
\crefname{section}{Section}{Sections}
\crefname{appendix}{Appendix}{Appendices}
\crefname{figure}{Fig.}{Figs.}
\crefname{table}{Table}{Tables}
% \crefname{algorithm}{Algorithm}{Algorithms}

@@

\newcommand{\CHSH}{CHSH^{(d)}}
\newcommand{\MS}{MS}
\newcommand{\SVT}{SVT}
\newcommand{\EPR}[1]{\Sigma^{(#1)}}
\newcommand{\paulix}{\sigma_x}
\newcommand{\pauliz}{\sigma_z}
\newcommand{\G}{G}
\newcommand{\LS}{LS}
\newcommand{\tM}{\tilde{M}}
\newcommand{\tN}{\tilde{N}}
\newcommand{\tA}{\tilde{A}}
\newcommand{\tB}{\tilde{B}}
\newcommand{\tX}{\tilde{X}}
\newcommand{\tZ}{\tilde{Z}}
\newcommand{\tU}{\tilde{U}}
\newcommand{\tW}{\tilde{W}}
\newcommand{\tx}{\tilde{x}}
\newcommand{\tpsi}{\tilde{\psi}}
\newcommand{\tri}{\Delta}
\newcommand{\lB}{\overline{B}}
\newcommand{\dr}[1]{d^{(#1)}}
\newcommand{\nr}{n(r)}
\newcommand{\mr}{m(r)}
\newcommand{\ux}{\underline{x}}
\newcommand{\uc}{\underline{c}}
\newcommand{\ua}{\underline{a}}

@@

\newtheorem{theorem}{Theorem}
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{proposition}[theorem]{Proposition}
\newtheorem{definition}[theorem]{Definition}
\newtheorem{corollary}[theorem]{Corollary}
\newtheorem{conjecture}[theorem]{Conjecture}
\newtheorem{claim}[theorem]{Claim}
\newtheorem*{conjecture*}{Conjecture}
\newtheorem*{problem}{Problem}
\newtheorem*{example}{Example}

@@

\title{Robust self-testing of large entanglement with constant alphabet}

@@

@@

\begin{table}[H]
\begin{center}
\begin{tabular}{|c|c||c|c|c|c|c|c|}
\hline
\multicolumn{2}{|c|}{} &
\multicolumn{6}{|c|}{$y=(\nr+1, r+6)$}\\
\cline{3-8}
\multicolumn{2}{|c|}{} &
$b = 00$ & $b=01$ & 
$b = 10$ & $b=11$ &
$b = \perp0$ & $b= \perp1$   \\
\hline
\hline
\multirow{3}{*}{$x = \nr+1$} & $a=0$ & $\frac{1}{2d-2}$ & $\frac{1}{2d-2}$ &  $0$
& $0$ & $0$ & $0$  \\
\cline{2-8}
&$a=1$ & $0$ & $0 $ & $\frac{1}{2d-2}$ 
&  $\frac{1}{2d-2}$ & $0$ & $0$  \\
\cline{2-8}
&$b=\perp$ & 0 & 0 & $0$ 
&  0 & $\frac{d-3}{2d-2}$ & $\frac{d-3}{2d-2} $  \\
\hline
\multirow{2}{*}{$x = r+6$} & $a=0$ & $\frac{1}{2d-2}$ & $0$ & $\frac{1}{2d-2}$ 
& $0$ & $\frac{d-3}{2d-2}$ & 0  \\
\cline{2-8}
&$a=1$ & $0$ & $\frac{1}{2d-2}$ & $0$ 
&  $\frac{1}{2d-2}$ & $0$ & $\frac{d-3}{2d-2}$  \\
\hline
\end{tabular}
\end{center}
\caption{The correlation for the commutation test between $M_{r+6}$ and $M_{\nr+1}$.}
\end{table}
The correlation table for the other $7$ commutation tests are similar.

@@

For simplicity, we define $O_A = M_1M_2$ and $U_A=M_3M_4$ such that
the conclusion of \cref{prop:lct_adv} can be rewritten as 
\begin{align}
	U_A^k O_A (U_A\ct)^k \ket{\psi} \appd{O(r^{k+1} \se)} O_A^{r^k} \ket{\psi}.
\end{align}
Similar relation holds on Bob's side too.

The other relations that are embedded in $\Gamma$ are 
\begin{align}
	\label{eq:comm}&[f_0, a_i] = [f_2, a_i] = [g_0, a_i] = [g_2, a_i] = e \text{ for all } i = 1 \dots r+5 \\
	\label{eq:mg1}&f_0g_0 = Jg_0f_0 \\
	\label{eq:mg2}&f_2g_2 = J g_2 f_2.
\end{align}
We summarize the implications in the following corollary.
\begin{proposition}
	\label{prop:lct_comm}
	Let $S$, $\{M_j, N_j\}_{j=1}^{\nr}$ be the strategy and observables defined in \cref{prop:lct_base},
	then
	\begin{align}
		&M_{r+6} M_j \ket{\psi} \appd{O(r\se)} M_j M_{r+6} \ket{\psi} && 
		M_{r+8}M_j \ket{\psi} \appd{O(r\se)} M_j M_{r+8} \ket{\psi} \\
		&M_{r+9} M_j \ket{\psi} \appd{O(r\se)} M_j M_{r+9} \ket{\psi} && 
		M_{r+11}M_j \ket{\psi} \appd{O(r\se)} M_j M_{r+11} \ket{\psi} 
	\end{align}
	for all $j = 1 \dots r+5$, and
	\begin{align}
		&M_{r+6}M_{r+9} \ket{\psi} \appd{O(r\se)} - M_{r+9}M_{r+6} \ket{\psi} \\
		&M_{r+8}M_{r+11} \ket{\psi} \appd{O(r\se)} -M_{r+11}M_{r+8} \ket{\psi}.
	\end{align}
\end{proposition}
Recall all the relations in \cref{eq:comm,eq:mg1,eq:mg2} are embedded in constant number of linear relations in $\Gamma$,
so this proposition can be proved using the same technique as that used in the proof of \cref{prop:lct_base}.

%-----------------------------------------------------------------
\subsection{Self-test}
%-----------------------------------------------------------------
\hl{This subsection needs to be formalized.}
We give a formal version of \cref{thm:pr_2} first and then prove it.
\begin{theorem}
\label{thm:selftest}
	If a quantum strategy using the shared state $\ket{\psi}$ achieves the ideal 2-party correlation $C(\dr{r})$ where $d$ is an odd
	prime number with primitive root $r \in \{2,3,5\}$, then there exist local isometries $\Phi_A$ and $\Phi_B$, and a state $\ket{junk}$ such 
	that $\Phi_A\x\Phi_B \ket{\psi} = \ket{\EPR{d-1}} \x \ket{junk}$.
\end{theorem}
\begin{proof}
Suppose Alice and Bob achieve the optimal correlation with the quantum strategy $(\ket{\psi}, \{A_x\}, \{B_y\})$
for all $x,y \in \calX \times \calY$ .
The observables $A_x$ and $B_y$ and the shared state $\ket{\psi}$ shall not be confused with the ones used in the optimal strategy.
By Lemma~$4.3$ of Ref.~\cite{coladan2017}, we can extract an operator solution from the perfect winning strategy 
of the linear system game $\LS_r$. 
For each variable $\{ x_i \}_{i=1}^{n_r}$, Alice and Bob has operators $A_i$ and $B_i$ respectively.
The condition that they agree with assignment to variables means that 
\begin{align}
	\bra{\psi} A_i \otimes \overline{B_i} \ket{\psi} = 1 \Rightarrow A_i \otimes \overline{B_i} \ket{\psi} = \ket{\psi}
	\text{ for } 1 \leq i \leq n_r
\end{align}
and the condition that Alice's assignments satisfy the constraint means that 
\begin{align}
	\Tr(\rho_A \Pi_{j: H(i,j) \neq 0} A_j) = \Tr(\rho_A) \text{ for all } 1 \leq i \leq m_r
\end{align}
where $\rho_A =  \Tr_B(\ketbra{\psi}{\psi})$. 
Similarly we define $\rho_B = \Tr_A(\ketbra{\psi}{\psi})$.
For any $\ket{v} \in \supp(\rho_A)$,
we have 
\begin{align}
\Pi_{j:H(i,j) \neq 0} A_j \ket{v} = \ket{v} \text{ for all } 1 \leq i \leq m_r.
\end{align}
Since the relation $uxu^{-1} = x^r$, where $r$ is the primitive root of $d$, is embedded in this linear system game, we know
\begin{align}
	A_3A_4 A_1A_2 (A_3A_4)^\dagger \ket{v}= (A_1A_2)^r \ket{v} \text{ for all } \ket{v} \in \supp(\rho_A).
\end{align}
For simplicity, we define $X_A = A_1A_2$ and $U_A=A_3A_4$ such that
the condition is equivalent to
\begin{align}
	\label{eq:ux_relation}
	U_AX_AU_A^\dagger \ket{v} = X_A^r \ket{v} \text{ for all } \ket{v} \in \supp(\rho_A).
\end{align}
We will come back to the implication of this condition later.

Suppose $A_{m_r+1} = A_\ast^\diamond- A_\ast^\perp = \Pi_{V_A} - \Pi_{V_A^\perp}$m, where $V_A$ is a
$2m$-dimensional vector space and $\Pi_{V_A}$ is the projector onto it. The reason why it has dimension $2m$
will be clear shortly. On Bob's side, we also have $B_{n_r+1} = B_\ast^\diamond- B_\ast^\perp = \Pi_{V_B} - \Pi_{V_B^\perp}$.
Recall that from the extended weighted CHSH test, we know
\begin{align}
	A_\ast^\diamond \ket{\psi} = B_\ast^\diamond \ket{\psi} = A_\ast^\diamond \x B_\ast^\diamond \ket{\psi},
\end{align}
which implies that with an appropriate change of basis, we can get $V_A = V_B$, so in the rest of the proof
we drop the subscript of $V$.
By \cref{lm:chsh_comp} and \cref{prop:2d-subspace}, we know $V$ consists of $\omega_d$-eigenvectors and $\omega_d^{-1}$ eigenvectors of 
$X_A$, so we can write 
\begin{align}
	\Pi_{V} = \Pi_{V_1} + \Pi_{V_{d-1}},
\end{align}
where $\Pi_{V_{1}}$ is the projector onto the $\omega_d$-eigenspace of $X_A$ and $\Pi_{V_{d-1}}$ is the projector 
onto the $\omega_d^{-1}$-eigenspace of $X_A$.
\hl{Here what we need is that $\Pi_{V_1,A} \ket{\psi} = \Pi_{V_{d-1},B} \ket{\psi} = \Pi_{V_1,A}\Pi_{V_{d-1},B}\ket{\psi}$
and $\Pi_{V_1,B} \ket{\psi} = \Pi_{V_{d-1},A} \ket{\psi} = \Pi_{V_1,B}\Pi_{V_{d-1},A}\ket{\psi}$.
This is not proved because $\Pi_{V_1}$ and $\Pi_{V_{d-1}}$ are not in the strategy.}
Suppose $\ket{x_{1}} \in V_{1}$, then $X_A \ket{x_{1}} = \omega_d \ket{x_{1}}$.
By \cref{eq:ux_relation} we can calculate that
\begin{align}
\label{eq:ladder}
 X_AU_A^\dagger \ket{x_{1}} = U_A^\dagger X_A^r \ket{x_{1}} = \omega_d^r U_A^\dagger \ket{x_{1}},
\end{align}
so $U_A^\dagger \ket{x_{1}}$ is an eigenvector of $X_A$ with eigenvalue $\omega_d^r$.
By induction, we know $X_A (U_A^\dagger)^i \ket{x_{1}} = \omega_d^{r^i} (U_A^\dagger)^i\ket{x_{1}}$. 
From the set $\{(U_A^\dagger)^i \Pi_{V_1} (U_A)^i \}_{i=0}^{d-2}$, we can identify $\Pi_{V_i}$ for $i = 1 \dots  d-1$
such that $\Pi_{V_i}$ is the projector onto the $\omega_d^i$-eigenspace of $X_A$,
\hl{Actually, we are not sure about the containment between $\supp((U_A\ct)^{\log_r(d-1)} \Pi_{V_1} U_A^{\log_r(d-1)})$ and 
$\supp(\Pi_{V_{d-1}})$, so we cannot say that $\Pi_{V_{d-1}} = (U_A\ct)^{\log_r(d-1)} \Pi_{V_1} U_A^{\log_r(d-1)}$.}
and 
\begin{align}
 \cup_{i \in [d-1]+1} V_i \subset \supp(\rho_A).
\end{align}
Since unitary transformation does not change the rank of a matrix, we know $\rank(\Pi_{V_1}) = \rank(\Pi_{V_{i}}) =N$
for $ i =1 \dots d-1$.
We pick a basis for $V_1$ such that 
\begin{align}
	\Pi_{V_1} =  \sum_{j=1}^m \ketbra{x_{1,j}}{x_{1,j}},
\end{align}
then we can construct 
\begin{align}
 \Pi_{V_i} = \sum_{j=1}^m \ketbra{x_{i,j}}{x_{i,j}},
\end{align}
where $\ket{x_{i,j}} = (U\ct)^{k_i} \ket{x_{1,j}}$ for $r^{k_i} \equiv i \pmod{d}$ and $1 \leq j \leq m$.
By \cref{eq:ux_relation} we also know that $U_A \ket{x_{i,j}} = \ket{x_{i/2,j}}$ for $i = 1,2 \dots d-1$.
In order to apply \cref{lm:ux_independ}, we construct $m$ subspaces $\{W_j\}_{j=1}^m$ where 
\begin{align}
	W_j = \spn( \{ \ket{x_{i,j}} \}_{i=1}^{d-1} )
\end{align}
The subspace $W_j$ is orthogonal to $W_{j'}$ for $j \neq j'$, and
$U_A$ and $X_A$ satisfy the condition of \cref{lm:ux_independ} when their actions are 
restricted to each $W_j$.
Similar argument also applies to operator $X_B$ and $U_B$ on Bob's side.

%Similar argument applies to Bob's operators. We can identify $X_B = B_1B_2$, 
%$U_B=B_3B_4$ and a vector space $S_B =\spn\{ \ket{x_{B,1}}, \ket{x_{B,2}} \dots  \ket{x_{B,d-1}} \} \subset \supp(\rho_B)$,
%such that 
%\begin{align}
%	X_B = \sum_{i=1}^{d-1} \omega_d^i \ketbra{x_{B,i}}{x_{B,i}} && U_B = \sum_{i=1}^{d-1} \ketbra{x_{B,i/2}}{x_{B,i}},
%\end{align}
%when their actions are restricted to $S_B$. Moreover, we can define a unitary $V: \supp{\rho_B} \to \supp(\rho_A)$,
%which maps $\ket{x_{B,i}}$ to $\ket{x_{A,i}}$ for $i=1\dots d-1$.

>>>>

% Clever references

\usepackage{cleveref}%[nameinlink]

\crefname{lemma}{Lemma}{Lemmas}
\crefname{proposition}{Proposition}{Propositions}
\crefname{definition}{Definition}{Definitions}
\crefname{theorem}{Theorem}{Theorems}
\crefname{conjecture}{Conjecture}{Conjectures}
\crefname{corollary}{Corollary}{Corollaries}
\crefname{claim}{Claim}{Claims}
\crefname{section}{Section}{Sections}
\crefname{appendix}{Appendix}{Appendices}
\crefname{figure}{Fig.}{Figs.}
\crefname{table}{Table}{Tables}

% \crefname{algorithm}{Algorithm}{Algorithms}

@@

\newcommand{\CHSH}{CHSH^{(d)}}
\newcommand{\MS}{MS}
\newcommand{\SVT}{SVT}
\newcommand{\EPR}[1]{\Sigma^{(#1)}}
\newcommand{\paulix}{\sigma_x}
\newcommand{\pauliz}{\sigma_z}
\newcommand{\G}{G}
\newcommand{\LS}{LS}
\newcommand{\tM}{\tilde{M}}
\newcommand{\tN}{\tilde{N}}
\newcommand{\tA}{\tilde{A}}
\newcommand{\tB}{\tilde{B}}
\newcommand{\tX}{\tilde{X}}
\newcommand{\tZ}{\tilde{Z}}
\newcommand{\tU}{\tilde{U}}
\newcommand{\tW}{\tilde{W}}
\newcommand{\tx}{\tilde{x}}
\newcommand{\tpsi}{\tilde{\psi}}
\newcommand{\tri}{\Delta}
\newcommand{\lB}{\overline{B}}
\newcommand{\dr}[1]{d^{(#1)}}
\newcommand{\nr}{n(r)}
\newcommand{\mr}{m(r)}
\newcommand{\ux}{\underline{x}}
\newcommand{\uc}{\underline{c}}
\newcommand{\ua}{\underline{a}}
\newcommand{\ub}{\underline{b}}

@@

\newtheorem{theorem}{Theorem}[section]
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{proposition}[theorem]{Proposition}
\newtheorem{definition}[theorem]{Definition}
\newtheorem{corollary}[theorem]{Corollary}
\newtheorem{conjecture}[theorem]{Conjecture}
\newtheorem{claim}[theorem]{Claim}
\newtheorem*{conjecture*}{Conjecture}
\newtheorem*{problem}{Problem}
\newtheorem*{example}{Example}

@@

\title{Robust self-testing of large entanglement with constant-sized correlations}

@@

%-----------------------------------------------------------
\subsection{Approximation tools}
%-----------------------------------------------------------
In the rest of the paper, we use the following approximation results implicitly and explicitly.
\begin{proposition}
	\label{prop:inner_pd}
	Let $\ket{v}$ and $\ket{v'}$ be vectors with length less than equal to $1$ satisfying the relation that $\ket{v} \appd{\epsilon} \ket{v'}$
	then for any unit vector $\ket{u}$,
	\begin{align}
		 \braket{v}{u} \appd{\ep} \braket{v'}{u} .
	\end{align}	
\end{proposition}
\begin{proof}
	We can write $\ket{v'} = \ket{v} + \ket{v''}$, where $\norm{\ket{v''}} \leq \epsilon$,
	then
	\begin{align}
	\norm{ \braket{v}{u} - \braket{v'}{u} } = \norm{\braket{v''}{u}} \leq \norm{\ket{u}}\norm{\ket{v''}} \leq \epsilon.
	\end{align}
\end{proof}
\begin{proposition}
	Let $\ket{u_i}$ and $\ket{v_i}$ for $i = 1,2$ be vectors with length less than equal to $1$
	such that 
	$\ket{u_1} \appd{\ep_1} \ket{v_1}$ and $\ket{u_2} \appd{\ep_2} \ket{v_2}$
	then 
	\begin{align}
		\braket{u_1}{u_2} \appd{\ep_1+ \ep_2} \braket{v_1}{v_2}.
	\end{align}
\end{proposition}
\begin{proof}
	By direct calculation we have
	\begin{align}
		\norm{ \braket{u_1}{u_2} - \braket{v_1}{v_2}} \leq &\norm{\braket{u_1}{u_2} - \braket{v_1}{u_2}}
		+ \norm{\braket{v_1}{u_2} - \braket{v_1}{v_2}} \\
		\leq & \ep_1 + \ep_2,
	\end{align}
	where we used \cref{prop:inner_pd}.
\end{proof}
\begin{proposition}
\label{prop:orthog}
	Let $H$ be a Hermitian matrix and $\ket{u}$ and $\ket{v}$ be two vectors with length less or equal to $1$,
	which satisfy the condition that 
	\begin{align}
		H\ket{u} \appd{\ep_1} a \ket{u}, \\
		H\ket{v} \appd{\ep_2} b \ket{v}, 
	\end{align}
	for some $a > b \in \R$, then
	\begin{align}
		\norm{\braket{u}{v}} \leq \frac{\ep_1+\ep_2}{a-b}.
	\end{align}
\end{proposition}
\begin{proof}
	We write $H\ket{u} = a\ket{u} + \ket{u'}$ such that $\norm{\ket{u'}} \leq \ep_1$.
	Similarly, we write $H\ket{v} = b\ket{v} + \ket{v'}$ such that $\norm{\ket{v'}} \leq \ep_2$.
	Then, we know
	\begin{align}
		\bra{v}H\ket{u} = a\braket{v}{u} + \braket{v}{u'},\\
		\bra{v}H\ket{u}  =b\braket{v}{u} + \braket{v'}{u},
	\end{align}
	Subtracting the second equation from the first equation gives us that 
	\begin{align}
		\norm{\braket{v}{u}} = \frac{\norm{\braket{v'}{u} -  \braket{v}{u'}}}{a-b} \leq \frac{\norm{\ket{v}}\norm{\ket{u'}}+
		\norm{\ket{u}}\norm{\ket{v'}}}{a-b} 
		\leq \frac{\ep_1+\ep_2}{a-b}.
	\end{align}
\end{proof}
\begin{proposition}
\label{prop:close_vec}
	Let $\ket{u}$ and $\ket{v}$ be two vectors such that $\norm{\ket{u}} \appd{\ep_1} 1$ and
	$\norm{\ket{v}} \appd{\ep_2} 1$ , if $\braket{u}{v} \geq 1 - \ep_3$,
	then
	\begin{align}
		\ket{u} \appd{O(\sqrt{\ep_1+\ep_2+\ep_3})} \ket{v}.
	\end{align}
\end{proposition}
\begin{proof}
	Direct calculation gives us that
	\begin{align}
		\norm{\ket{u} - \ket{v}}^2 &= \norm{\ket{u}}^2 + \norm{\ket{v}}^2 - 2\braket{u}{v} \\
		&\leq (1+\ep_1)^2 + (1+\ep_2)^2 - 2(1 - \ep_3)\\
		&= 2(\ep_1+\ep_2+\ep_3)+ \ep_1^2 + \ep_2^2\\
		& = O(\ep_1+\ep_2+\ep_3).
	\end{align}
\end{proof}
\begin{proposition}
	Let $\ket{u}$ be a vector with length less or equal to $1$ such that for a unitary $U$,
	\begin{align}
		U\ket{u} \appd{\ep} a\ket{u} \text{ for } a \in \C,
	\end{align}
	then
	\begin{align}
		U^n \ket{u} \appd{n\ep} a^n \ket{u} \text{ for all } n \geq 1.
	\end{align}
\end{proposition}
\begin{proof}
	We can prove it by induction. 
	For $n=1$, the statement is satisfied.
	Assume it holds for $n = k-1$ and consider $n = k$, then we have
	\begin{align}
		&\norm{U^k \ket{u} - a^k\ket{u}} \\
		\leq &\norm{U} \norm{U^{k-1} \ket{\psi} - a^{k-1}\ket{\psi}} + \norm{a^{k-1}}
		\norm{U\ket{\psi} - a \ket{\psi}}\\
		\leq &(k-1)\ep + \ep = k \ep,
	\end{align}
	where we used the fact that $\norm{U} = 1$ and $\norm{a} \leq 1$.
\end{proof}

@@

\begin{table}[H]
\begin{center}
\begin{tabular}{|c|c||c|c|c|c|c|c|}
\hline
\multicolumn{2}{|c|}{} &
\multicolumn{6}{|c|}{$y=(\nr+1, r+6)$}\\
\cline{3-8}
\multicolumn{2}{|c|}{} &
$b = 00$ & $b=01$ & 
$b = 10$ & $b=11$ &
$b = \perp0$ & $b= \perp1$   \\
\hline
\hline
\multirow{3}{*}{$x = \nr+1$} & $a=0$ & $\frac{1}{2d-2}$ & $\frac{1}{2d-2}$ &  $0$
& $0$ & $0$ & $0$  \\
\cline{2-8}
&$a=1$ & $0$ & $0 $ & $\frac{1}{2d-2}$ 
&  $\frac{1}{2d-2}$ & $0$ & $0$  \\
\cline{2-8}
&$b=\perp$ & 0 & 0 & $0$ 
&  0 & $\frac{d-3}{2d-2}$ & $\frac{d-3}{2d-2} $  \\
\hline
\multirow{2}{*}{$x = r+6$} & $a=0$ & $\frac{1}{2d-2}$ & $0$ & $\frac{1}{2d-2}$ 
& $0$ & $\frac{d-3}{2d-2}$ & 0  \\
\cline{2-8}
&$a=1$ & $0$ & $\frac{1}{2d-2}$ & $0$ 
&  $\frac{1}{2d-2}$ & $0$ & $\frac{d-3}{2d-2}$  \\
\hline
\end{tabular}
\end{center}
\caption{The correlation for the commutation test between $M_{r+6}$ and $M_{\nr+1}$.}
\label{tbl:comm}
\end{table}
The correlation table for the other $7$ commutation tests are similar.

@@

For simplicity, we define $O_A = M_1M_2$ and $U_A=M_3M_4$ such that
the conclusion of \cref{prop:lct_adv} can be rewritten as 
\begin{align}
	U_A^k O_A (U_A\ct)^k \ket{\psi} \appd{O(r^{k+1} \se)} O_A^{r^k} \ket{\psi}.
\end{align}
On Bob's side, we also define $O_B = N_1N_2$ and $U_B = N_3N_4$ 
and similar relations hold.

The other relations that are embedded in $\Gamma$ are 
\begin{align}
	\label{eq:comm}&[f_0, a_i] = [f_2, a_i] = [g_0, a_i] = [g_2, a_i] = e \text{ for all } i = 1 \dots r+5 \\
	\label{eq:mg1}&f_0g_0 = Jg_0f_0 \\
	\label{eq:mg2}&f_2g_2 = J g_2 f_2.
\end{align}
We summarize the implications in the following corollary.
\begin{proposition}
	\label{prop:lct_comm}
	Let $S$, $\{M_j, N_j\}_{j=1}^{\nr}$ be the strategy and observables defined in \cref{prop:lct_base},
	then
	\begin{align}
		&M_{r+6} M_j \ket{\psi} \appd{O(r\se)} M_j M_{r+6} \ket{\psi} && 
		M_{r+8}M_j \ket{\psi} \appd{O(r\se)} M_j M_{r+8} \ket{\psi} \\
		&M_{r+9} M_j \ket{\psi} \appd{O(r\se)} M_j M_{r+9} \ket{\psi} && 
		M_{r+11}M_j \ket{\psi} \appd{O(r\se)} M_j M_{r+11} \ket{\psi} 
	\end{align}
	for all $j = 1 \dots r+5$, and
	\begin{align}
		&M_{r+6}M_{r+9} \ket{\psi} \appd{O(r\se)} - M_{r+9}M_{r+6} \ket{\psi} \\
		&M_{r+8}M_{r+11} \ket{\psi} \appd{O(r\se)} -M_{r+11}M_{r+8} \ket{\psi}.
	\end{align}
\end{proposition}
Recall all the relations in \cref{eq:comm,eq:mg1,eq:mg2} are embedded in constant number of linear relations in $\Gamma$,
so this proposition can be proved using the same technique as that used in the proof of \cref{prop:lct_base}.
%------------------------------------------------------------------------------------------
\subsection{Implication of passing the extended weighted CHSH test}
\label{sec:imp_chsh}
%------------------------------------------------------------------------------------------
\begin{proposition}
\label{prop:chsh_base}
Let $S$ be an $\ep$-approximate quantum strategy,
then the strategy $S$ satisfy the following relations
\begin{align}
	  M_\ast^\diamond N_\ast^\diamond \ket{\psi}
	  \appd{O( r\se)}&M_\ast^\diamond \ket{\psi} \appd{O( r\se)} (M_{\nr+1}^0+M_{\nr+1}^1)\ket{\psi} \appd{O( r\se)} (M_{\nr+2}^0+M_{\nr+2}^1)\ket{\psi} \\
	  \appd{O( r\se)}&N_\ast^\diamond \ket{\psi} \appd{O( r\se)} (N_{\nr+1}^0+N_{\nr+1}^1)\ket{\psi} \appd{O( r\se)} (N_{\nr+2}^0+N_{\nr+2}^1)\ket{\psi}\\
	M_\ast^\perp N_\ast^\perp\ket{\psi}\appd{O( r\se)} &M_\ast^\perp\ket{\psi} \appd{O( r\se)} M_{\nr+1}^\perp \ket{\psi} \appd{O( r\se)} M_{\nr+2}^\perp \ket{\psi}\\
	\appd{O( r\se)}&N_\ast^\perp\ket{\psi} \appd{O( r\se)} N_{\nr+1}^\perp \ket{\psi} \appd{O( r\se)} N_{\nr+2}^\perp \ket{\psi}.
\end{align}
and
\begin{align}
&M_{\nr+1}^0 \ket{\psi} \appd{O( r\se)} N_{\nr+1}^0 \ket{\psi} && M_{\nr+1}^1\ket{\psi} \appd{O( r\se)} N_{\nr+1}^1 \ket{\psi}\\
&M_{\nr+2}^0 \ket{\psi} \appd{O( r\se)} N_{\nr+2}^0 \ket{\psi} && M_{\nr+2}^1\ket{\psi} \appd{O( r\se)} N_{\nr+2}^1 \ket{\psi}.
\end{align}
\end{proposition}

\begin{proof} 
Recall that the implication of $S$ being an $\ep$-approximate strategy is that 
$\pr{ab}{xy} \appd{O(r^2\ep)} \tpr{ab}{xy}$. 
We prove $(M_{\nr+1}^0+M_{\nr+1}^1)\ket{\psi} \appd{O(r\se)} N_\ast^\diamond \ket{\psi}$ as an example.
The rest of the relations follow the same line of arguments.
From the correlation, we can observe that
\begin{align*}
 \bra{\psi} (M_{\nr+1}^0+M_{\nr+1}^1)N_\ast^\diamond \ket{\psi} = \frac{2}{d-1} - O(r^2 \epsilon).
\end{align*}
On the other hand, the correlation also tells us that 
\begin{align*}
	\bra{\psi} N_\ast^\diamond \ket{\psi} \appd{O(r^2\epsilon)} 
 \bra{\psi}(M_{\nr+1}^0+M_{\nr+1}^1)\ket{\psi} \appd{O(r^2\epsilon)} \frac{2}{d-1},
\end{align*}
which implies that 
\begin{align*}
	&\norm{(M_{\nr+1}^0 + M_{\nr+1}^1) \ket{\psi} - N_\ast^\diamond\ket{\psi}}^2 \\
	= &\bra{\psi} N_\ast^\diamond \ket{\psi}+\bra{\psi}(M_{\nr+1}^0+M_{\nr+1}^1)\ket{\psi} - 2\bra{\psi}N_\ast^\diamond(M_{\nr+1}^0 + M_{\nr+1}^1)N_\ast^\diamond \ket{\psi}\\
	= &O(r^2 \epsilon),
\end{align*}
where we used the fact that $(M_{\nr+1}^0 + M_{\nr+1}^1)^2 = M_{\nr+1}^0 + M_{\nr+1}^1$.
Hence we can conclude that $(M_{\nr+1}^0 + M_{\nr+1}^1)N_\ast^\diamond \ket{\psi} \appd{O(r\se)} N_\ast^\diamond\ket{\psi}$.
%From the correlation, we know that 
%\begin{align}
%	\bra{\psi} M_\ast^\perp N_\ast^\perp \ket{\psi} = \frac{d-3}{d-1} - O(r^2 \ep).
%\end{align}
%In the mean time, we also have 
%$\norm{M_\ast^\perp \ket{\psi}}^2 \appd{O(r^2\ep)} \norm{N_\ast^\perp\ket{\psi}}^2 \appd{O(r^2\ep)} (d-3)/(d-1)$.
%The two facts above imply that 
%\begin{align}
%	\norm{M_\ast^\perp \ket{\psi} - N_\ast^\perp \ket{\psi}}^2 = \norm{M_\ast^\perp \ket{\psi}}^2 + \norm{N_\ast^\perp \ket{\psi}}^2
%	- 2 \bra{\psi} M_\ast^\perp N_\ast^\perp \ket{\psi}  = O(r^2 \ep),
%\end{align}
%or equivalently,
%\begin{align}
%	M_\ast^\perp \ket{\psi} \appd{O(r\se)} N_\ast^\perp \ket{\psi}.
%\end{align}
\end{proof}

%Another conclusion we can draw is that $B_\ast^\diamond = A_\ast^\diamond$ and $B_\ast^\perp = A_\ast^\perp$.
%We can assume the Schmidt decomposition of $\ket{\psi}$ is
%\begin{align}
%	\ket{\psi} = \sum_{i=1}^d \lambda_i \ket{i}\ket{i}.
%\end{align}
%If $\supp{A_\ast^\diamond} \neq \supp{B_\ast^\diamond}$, then $B_\ast^\diamond\ket{\psi} \neq A_\ast^\diamond\ket{\psi}$. Since $B_\ast^\diamond$ and $A_\ast^\diamond$ are projectors,
%By the orthogonality relations, we can also conclude that $A_\ast^\perp = B_\ast^\perp$.

%Maybe we can first conclude that $\spn(A_0^0+A_0^1) = \spn(A_1^0+A_1^1) = \spn(A_\ast^\diamond)$.
\begin{proposition}
	\label{prop:s1s2}
	Let $S$ be an $\ep$-approximate strategy. We define
		&M_{\nr+1} = M_{\nr+1}^0 - M_{\nr+1}^1 && M_{\nr+2} = M_{\nr+2}^0 - M_{\nr+2}^1,\\
		&N_{\nr+1} = N_{\nr+1}^0 - N_{\nr+1}^1 && N_{\nr+2} = N_{\nr+2}^0 - N_{\nr+2}^1.
	Then $S$ induces two strategies that achieve $\ip{\I_{\cot(-\pi/d)}}_{\max} - O(d r\se)$, which are
		S_1 = \left(M_{\nr+1}, M_{\nr+2}, N_1, N_2, \frac{M_\ast^\diamond\ket{\psi}}{\norm{M_\ast^\diamond\ket{\psi}}}\right),\\
		S_2 = \left(N_{\nr+1}, N_{\nr+2}, M_1, M_2, \frac{M_\ast^\diamond\ket{\psi}}{\norm{M_\ast^\diamond\ket{\psi}}}\right).
\end{proposition}
\begin{proof}
We will prove that $\bra{\psi} M_{\nr+1}^0N_1^0 \ket{\psi} \appd{O(\sd r\se)} \bra{\psi}M_\ast^\diamond M_{\nr+1}^0N_1^0 M_\ast^\diamond\ket{\psi}$ as an example,
	   \bra{\psi} M_{\nr+1}^0N_1^0 \ket{\psi} 
	= &\bra{\psi}(M_\ast^\diamond + M_\ast^\perp) M_{\nr+1}^0N_1^0 (M_\ast^\diamond + M_\ast^\perp)\ket{\psi} \\
	= & \bra{\psi}M_\ast^\diamond M_{\nr+1}^0N_1^0 M_\ast^\diamond\ket{\psi} + \bra{\psi}M_\ast^\diamond M_{\nr+1}^0N_1^0 M_\ast^\perp\ket{\psi}\\
	&+\bra{\psi}M_\ast^\perp M_{\nr+1}^0N_1^0 M_\ast^\diamond\ket{\psi} + \bra{\psi}M_\ast^\perp M_{\nr+1}^0N_1^0 M_\ast^\perp\ket{\psi}\\
	\appd{O(r\se)}&  \bra{\psi}M_\ast^\diamond M_{\nr+1}^0N_1^0 M_\ast^\diamond\ket{\psi} + \bra{\psi}M_\ast^\diamond M_{\nr+1}^0N_1^0 M_{\nr+1}^\perp\ket{\psi} \\
	&+\bra{\psi}M_{\nr+1}^\perp M_{\nr+1}^0N_1^0 M_\ast^\diamond\ket{\psi} + \bra{\psi}M_{\nr+1}^\perp M_{\nr+1}^0N_1^0 M_{\nr+1}^\perp\ket{\psi}\\
	=&\bra{\psi}M_\ast^\diamond M_{\nr+1}^0N_1^0 M_\ast^\diamond\ket{\psi},
